Assessing the Impact of Vision Zero on Traffic Collisions in Toronto Neighborhoods (2014–2021):

### 2024-12-04 paper/paper.qmd
Paper Done!

- **Underreporting and Data Bias**: Minor collisions or those without injuries may be underreported. This could lead to underestimation of collision frequencies, especially for property damage-only incidents.
- **Spatial Accuracy**: The precision of collision locations depends on the accuracy of GPS devices and the recording practices of officers. Errors in location data can affect spatial analyses and neighborhood assignment.
- **Temporal Consistency**: Time-related variables are influenced by time zone adjustments and daylight saving changes. Ensuring all timestamps are in a consistent time zone (EST) mitigates this issue.
- **Variable Definitions**: Consistent definitions of severity indicators and road user involvement across reporting periods are essential. Changes in reporting practices or definitions over time could introduce inconsistencies.
- **Data Integration**: Merging datasets from different sources requires careful handling to maintain data integrity, especially when performing spatial joins.

@@

The model was implemented using the `glm.nb()` function from the `MASS` package in R (Venables and Ripley, 2002). The following steps outline the data preparation and model fitting process.

@@

```{r setup, include=FALSE}
   # Load necessary libraries
   library(tidyverse)
   library(MASS)
   library(ggplot2)
   library(caret)
   library(here)

@@

The model estimates are presented in **Table 1**.

```{r model-results, echo=FALSE, message=FALSE}
#| message: false

@@

The estimated coefficients from the Negative Binomial regression model are summarized in **Table 1**.

**Table 1: Negative Binomial Regression Estimates**

@@

To assess the model fit, we conducted a residual analysis by plotting the Pearson residuals against the fitted values (Figure 1).

```{r residual-plot-2, fig.cap="Residuals vs. Fitted Values", echo=FALSE}
# Plot residuals vs. fitted values
residuals <- residuals(nb_model, type = "pearson")
fitted_values <- fitted(nb_model)

@@

This study aimed to identify significant predictors of traffic collision counts across Toronto neighborhoods from 2014 to 2021 and assess the impact of the Vision Zero Road Safety Plan implemented in 2017. The Negative Binomial regression model was employed due to overdispersion in the collision count data, providing more reliable estimates than the Poisson model.

>>>>

- **Underreporting and Data Bias**: Minor collisions or those without injuries may be underreported. This could lead to underestimation of collision frequencies, especially for property damage-only incidents [@Elvik1999; @Alsop2001].
- **Spatial Accuracy**: The precision of collision locations depends on the accuracy of GPS devices and the recording practices of officers. Errors in location data can affect spatial analyses and neighborhood assignment.
- **Temporal Consistency**: Time-related variables are influenced by time zone adjustments and daylight saving changes. Ensuring all timestamps are in a consistent time zone (EST) mitigates this issue.
- **Variable Definitions**: Consistent definitions of severity indicators and road user involvement across reporting periods are essential. Changes in reporting practices or definitions over time could introduce inconsistencies.
- **Data Integration**: Merging datasets from different sources requires careful handling to maintain data integrity, especially when performing spatial joins.

@@

The model was implemented using the glm.nb() function from the MASS package in R [@MASS].

@@

```{r setup, include=FALSE}
#| echo: false
   # Load necessary libraries
   library(tidyverse)
   library(MASS)
   library(ggplot2)
   library(caret)
   library(here)

@@

The model estimates are presented in the Table below.

```{r model-results, echo=FALSE, message=FALSE}
#| label: tab:model-estimates
#| echo: false
#| message: false

@@

The estimated coefficients from the Negative Binomial regression model are summarized in **Table NB**.

**Table NB: Negative Binomial Regression Estimates**

@@

To assess the model fit, we conducted a residual analysis by plotting the Pearson residuals against the fitted values  @ref(tab:residual-plot-1).

```{r residual-plot-2, fig.cap="Residuals vs. Fitted Values", echo=FALSE}
#| label: tab:residual-plot-1
# Plot residuals vs. fitted values
residuals <- residuals(nb_model, type = "pearson")
fitted_values <- fitted(nb_model)

@@

This study aimed to identify significant predictors of traffic collision counts across Toronto neighborhoods from 2014 to 2021 and assess the impact of the Vision Zero Road Safety Plan implemented in 2017. The Negative Binomial regression model was employed due to overdispersion in the collision count data, providing more reliable estimates than the Poisson model[@Hilbe2011].
